Lnc34a CAGE

### 2017-12-01 inst/lnc34a_cage/lnc34a_cage.Rmd
commented figure pdf save

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure4a"][[1]])
ggsave(
  plot = g,
  filename = path,
  device = cairo_pdf,
  height = 100,
  width = 90,
  units = "mm"
)
```

>>>>

# path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure4a"][[1]])
# ggsave(
#   plot = g,
#   filename = path,
#   device = cairo_pdf,
#   height = 100,
#   width = 90,
#   units = "mm"
# )
```
